%this assumes that res_yy.sty is in some path
\documentstyle[url, hyperref, margin, line]{res_yy}

\hypersetup{backref,pdfpagemode=Full,colorlinks=true,backref}

\addtolength{\oddsidemargin}{-0.45in}
\addtolength{\voffset}{-0.15in}
\addtolength{\textwidth}{1.00in} \addtolength{\textheight}{1.50in}

\renewcommand{\namefont}{\LARGE\emph}

\begin{document}

\name{Kyle Davis}
\address{kyldvs@gmail.com}

\begin{resume}

%\section{\textsc{Objective}}
%
%To utilize my graphic design experience for the purposes of creating visually appealing %marketing material for Midtown Assistance Center.

\section{\textsc{Education}}

\textbf{Georgia Institute of Technology} \hfill \emph{Fall 2013 - (Fall 2014)} \\
Masters in Computer Science \\
\newline
\textbf{Georgia Institute of Technology} \hfill \emph{Fall 2010 - Spring 2013} \\
Bachelor of Science in Computer Science \hfill GPA: 3.53 \\
\newline
\textbf{Kennesaw State University} \hfill \emph{Fall 2009 - Spring 2010} \\
Joint Enrollment Program (in lieu of my senior year at high school) \hfill GPA: 3.89

\section{\textsc{Skills}}

\small{\textbf{Skilled}: }\normalsize{Java}\\
\small{\textbf{Familiar}: }\normalsize{Linux, Javascript, HTML 5}\\
\small{\textbf{Exposure}: }\normalsize{Git, \LaTeX, Databases, PHP, C, Photoshop}

\begin{formatb}
  \employer{l}\dates{r}\\
  \location{l}\\
  \body\\
\end{formatb}

\section{\textsc{Experience}}

\employer{\textbf{Facebook}}
\dates{\emph{Summer 2013}}
\location{\emph{Software Engineer Intern}}
\begin{position}
Built a new advertiser homepage panel. My project was built in Javascript and React. The panel is displayed directly on the homepage of Facebook, and features statistics about how your advertisements are performing. The statistics that are displayed update in real time and are custimizable.
\end{position}

\employer{\textbf{Palantir Technologies}}
\dates{\emph{Summer 2012}}
\location{\emph{Software Engineer Intern}}
\begin{position}
Worked as the main front end developer on Phoenix Explorer. Phoenix Explorer is an application used to perform in memory analysis of many items that are the result of a database query. My main tasks were improving user experience, designing an API, and consuming the API. Did limited work on the back end as well.
\end{position}

\employer{\textbf{Georgia Institute of Technology}}
\dates{\emph{Spring 2011 - Present}}
\location{\emph{Head Teaching Assistant}}
\begin{position}
Teaching Assistant (TA) for the professor teaching Data Structures and Algorithms. Responsibilities include teaching recitation and holding weekly office hours. Have been a guest lecturer for the course. Head TA since Spring 2012. Extra responsibilities include managing 8-10 other TA and coordinating weekly assignments among them.
\end{position}

%%
%% We use the same formatting for projects as for work experience
%% Shown below is the formatting used previously
%%
%%  \begin{formatb}
%%    \employer{l}\title{r}\\
%%    \location{l}\dates{r}\\
%%    \body\\
%%  \end{formatb}
%%
%%
%%  Note that \location is now being used for non-location information
%%
%%  This section could also use more formatting, but looks ok, as is
%%
%%
%% Note that we're redefining the formatting
%% We only have one row of information now, instead of two
%%

\section{\textsc{Research}}

\begin{formatb}
  \employer{l}\dates{r}\\
  \body\\
\end{formatb}

\employer{\textbf{Vehicle Routing}}
\dates{\emph{Spring 2013 - Present}}
\begin{position}
Researching with Professors Henrik Christensen, and Prasad Tetali to develop and test algorithms that can route multiple vehicles through warehouses with many obstacles. (This work resulted in a publication in the GT Tower)
\end{position}

\employer{\textbf{3D Bin Packing}}
\dates{\emph{February 2012 - Present}}
\begin{position}
Researching with Professors Henrik Christensen, and Prasad Tetali to develop software that empirically tests algorithms we design to efficiently pack boxes onto several pallets.
\end{position}

% \employer{\textbf{Independent Sets in Grid Graphs}}
% \dates{\emph{December 2011 - May 2012}}
% \begin{position}
% Researched with Professor Eric Vigoda. Worked on estimating bounds on properties of independent sets in grid graphs using Markov Chains and the coupling from the past technique.
% \end{position}

\section{\textsc{Activities}}

\begin{formatb}
  \employer{l}\dates{r}\\
  \body\\
\end{formatb}

\employer{\textbf{Georgia Tech Programming Team Coach}}
\dates{\emph{Fall 2010 - Present}}
\begin{position}
% President since \hfill \emph{Fall 2012} \\
% Coach since \hfill \emph{Fall 2013} \\
Competed in and practiced for programming contests in the GT Programming team. Helped build team skills by working on teams that were required to share a computer amongst 3 people during contests. Regularly gave lectures on challenging algorithmic topics to a group of around 30 students. (became president in Fall 2012, coach in Fall 2013)
\end{position}

% \employer{\textbf{TopCoder}}
% \dates{\emph{Fall 2010 - Present}}
% \begin{position}
% Compete in online competitions through topcoder.com \small{(user: Thirtyate)}.
% \end{position}

%\employer{\textbf{99 Designs}}
%\dates{\emph{Summer 2009}}
%\begin{position}
%Competed in graphic design contests through the website 99designs.com, a website designed to connect freelance designers with graphic design work. Username: Thirtyate, Portfolio: \href{http://99designs.com/people/thirtyate/folio}{[1]}
%\end{position}

%\employer{\textbf{Graphic Design}}
%\dates{\emph{Summer 2007 - Present}}
%\begin{position}
%Have worked with Photoshop doing graphic design as a hobby since highschool. Some of my work can be seen on my website: \href{http://www.kyldvs.com/images/robot.png}{[2]} \href{http://www.kyldvs.com/images/bubble.jpg}{[3]}
%\end{position}


%\employer{\textbf{Computer Science Tutor}}
%\dates{Fall 2009 - Spring 2010}
%\begin{position}
%Assisted students at Kennesaw State University with computer science topics.
%\end{position}

%%
%% Awards
%%

\section{\textsc{Awards}}

\begin{formatb}
  \employer{l}\dates{r}\\
  \body\\
\end{formatb}

\employer{\textbf{Barracuda 2011 Programming Competition}}
\dates{\emph{November 2011}}
\begin{position}
Won first place and $\$3,141$ in an AI based programming competition hosted by Barracuda Networks at Georgia Tech.
\end{position}

% \employer{\textbf{Mercer Spring 2011 Programming Competition}}
% \dates{\emph{Spring 2011}}
% \begin{position}
% Won first place in this annual, statewide, programming competition that simulates the ACM ICPC regional programming competition.
% \end{position}

\employer{\textbf{KSU Outstanding JEHP Student Award}}
\dates{\emph{Fall 2009}}
\begin{position}
This award was for being the student with the highest GPA in the largest number of credit hours
and honors courses participating in the Joint Enrollment Honors Program (JEHP) at Kennesaw
State University (KSU).
\end{position}

%%
%% Nothing special here, just a normal table
%%

% \section{\textsc{Course Work}}
% \begin{tabular}{lllll}
% Advanced Algorithms & \ \ & Combinatorics & \ \ & Linear Algebra\\
% Honors Algorithms & \ \ & Objects and Design & \ \ & Logic and Proofs\\
% Graph Theory & \ \ & Computer Organization & \ \ & Calculus 1-3\\
% Mathematical Problem Solving & \ \ & Data Structures & \ \ & German 1\\
% \end{tabular}

\end{resume}
\end{document}